Cybercrime and Online Video Games

### 2019-12-14 paper/paper.tex
Update paper.tex
new pdf
updated pqper + pdf

@@

Each algorithm gives each comment a probability to be either positive, negative or neutral. It also classifies whether a comment 
involves a trade or a Q\&A with the thread poster. We sum each algorithm's score 
and determine based on that score whether the comment is 
positive, negative or neutral. Below are charts showing the percentage of comments that were deemed positive, negative and neutral, 
percentage of comments involving a trade and percentage of comments with a Q\&A.

@@

@@

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{DistributionFortniteAge.png}
	\caption{Fortnite Age Distribution}
\end{figure} \cite{distribage}

@@

Each algorithm gives each comment a probability to be either positive, negative or neutral. It also classifies whether a comment 
involves a trade or a Q\&A with the thread poster. We sum each algorithm's score 
and determine based on that score whether the comment is positive,
negative or neutral. Below are charts showing the percentage of comments that 
were deemed positive, negative and neutral, percentage of comments involving a 
trade and percentage of comments with a Q\&A. For the trade and Q\&A charts, a 
one represents a trade or Q\&A and a zero represents no trade of Q\&A.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{TradeChart.png}
	\caption{Trade Chart}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{Q&AChart.png}
	\caption{Q\&A Chart}
\end{figure}

@@

The distribution of the Sentiment Analysis chart shows that while neutral comments may take up a plurality of the comments, no sentiment
is able to take up the majority of the overall comments. As for the positive or negative comments, while there might be more negative,
the distribution is promising considering the data was taken from a hack forum. For the trade chart it actual gives minimal
information. through manual thread analysis, we saw that the most common way of initiating a trade is through private messaging so while
the number of trades does not seem like a lot, many trades could have been done outside of the thread. Last but not least is the Q\&A
graph. This graph shows the general interest level of the community with regards to the different products and services offered. The 
interest rate is higher than the trade rate, by a lot, but this is still not quite representative of the data as many people utilize
private messaging for communication, though open thread questions about the product are still popular before PMing the seller.
